### 2019-07-11 bp_discussion.tex
small change in discussion section

%!TEX root = bioPrediction_main.tex
\section{Discussion}
%\vspace{0.05in}
\noindent
\textbf{Implications for HCI Design and Workspaces:}
The results discussed in this paper establish great potential
to increase the well-being of knowledge workers and the quality of their work
through monitoring their biometric signals and computer interactions with the
goal of recognizing their stress, awakeness, and focus levels in an uninvasive 
and automatic manner. Being able to accurately recognize periods of high-
stress in workers enables companies to prevent or de-escalate potentially 
dangerous situations in the workplace, e.g. confrontation between co-workers; 
or it can help to design more team-based approaches such as an 
awareness dashboard of a teams’ stress level.
Similarly, awakeness and focus
can be enhanced given such a technology
e.g. through individual approaches such as adapting the lighting in a control 
room, or scheduling breaks to prevent focus loss.

>>>>

%!TEX root = bioPrediction_main.tex
\section{Discussion}
%\vspace{0.05in}
\noindent
\textbf{Implications for HCI Design and Workspaces:}
The results discussed in this paper establish great potential
to increase the well-being of knowledge workers and the quality of their work
through monitoring their biometric signals and computer interactions with the
goal of recognizing their stress, awakeness, and focus levels in an uninvasive 
and automatic manner. Being able to accurately recognize periods of high-
stress in workers enables companies to prevent or de-escalate potentially 
dangerous situations in the workplace, e.g. confrontation between co-workers. Similarly, this can help to design more team-based approaches such as an 
awareness dashboard of a team's stress level, and avoid digital interruptions in high-stress or high-focus periods similar to previous studies~\cite{zuger2017reducing}.
Likewise, awakeness and focus
can be enhanced given such a technology
through individual approaches such as adapting the lighting in a control 
room, or scheduling breaks to prevent focus loss.
